---
title       : NBA Player Size Comparison App
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## NBA Player Size Comparison Comparison Application

<br>

<h3>1. See how the size of NBA players has changed over the years between 1947 and 2014</h3>
<h3>2. Visual displeay of the development</h3>
<h3>3. Free and available NOW!</h3>

--- .class #id 

## Ever wonder how big those guys are?

<h3>We all know those buys are big! But how big? And how has it changed over the eyears?</h3>
<br>
<h3>Now you can look at the development graphically and see how the player size has chaged over the years. Easy to use with a simple and intuitive web user interface.</h3>
<br>
<h3>All this and for free!</h3>

---
## Easy to use application with simple pull-down menu

<br>
Easy way to select the physical attribute of the player and see how that's developed over the years. The the data available covers following attributes:

- Age
- Height
- Weight
- Body-Mass Index (BMI)

You can even choose to see the rookies separately

---
## The Application

```{r echo=FALSE, error=FALSE}
load("Totals.Rda")
require(ggplot2)
```
Example picture generated on the fly:

```{r echo=FALSE, error=FALSE, fig.width=7, fig.height=6}
title = "Age of Players"
ylabel <- "Age (years)"
p <- ggplot(totals[totals$Rookie=="Everyone",], aes(x=Year, y=Age)) + geom_point(colour="blue")
p <- p + stat_smooth(method="loess")
p <- p + ggtitle(title) + ylab(ylabel)
p <- p + labs(colour = "Players")
p <- p + scale_x_continuous(breaks=seq(1950, 2010, 10))
p <- p + theme(text = element_text(size=20), 
               title = element_text(size=20))
print(p)

        
```


To try it out, go to <a href="https://tksf.shinyapps.io/Basketball_Project/">NBA Player Size Comparison App!</a>

